Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-24 article.tex
link between min dep graph and G

Our approach implicitly makes the additional assumption  that $P_X$ is  a joint
Gaussian distribution since it  outputs as  degree of association between two
neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$. Note also that
the partial correlation statistic is symmetric  (i.e., $\rho_{X_i, X_j |
X^{-i,j}} = \rho_{X_j, X_i | X^{-j,i}}$) and therefore does not account for the
direction of the interaction.

>>>>

Our approach implicitly makes the additional assumption  that $P_X$ is  a
joint Gaussian distribution since it  outputs as  degree of association
between two neurons $i$ and $j$ an estimate of $\rho_{X_i, X_j | X^{-i,j}}$.
Moreover, this minimal dependency graph will be close to G undirected
especially as this assumption is true. Note also that the partial correlation
statistic is symmetric  (i.e., $\rho_{X_i, X_j | X^{-i,j}} = \rho_{X_j, X_i |
X^{-j,i}}$) and therefore does not account for the direction of the
interaction without impacting the performance. The interest to not consider directivity will be discussed in section~\ref{sec:results}.
